Tests
\begin{itemize}
  \item Navigation Buttons
  \begin{itemize}
   \item Zoom in/out
   \item Pan(north, south, east, west)
   \end{itemize}
  \item Boundaries 
  \begin{itemize}
    \item Minimum zoom
    \item Maximum zoom
    \item Pan out of map(north, south, east, west) 
   \end{itemize}
  \item Hotkeys
  \begin{itemize}
   \item ESCAPE (reset to full view)
   \item C (clear all markers)
   \item I (zoom in)
   \item O (zoom out)
   \item Arrows (up, down, left, right)
  \end{itemize}
  \item Pathfinding 
  \begin{itemize}
   \item Place marker
   \item Two markers
   \item Two markers (same node)
   \item Multiple markers
   \item Clear markers (screen button)
   \item Switch between modes (recalculate route)
   \item Closest node (that fits current mode)
   \item Cannot travel opposite on one-way streets
  \end{itemize}
  \item Resizing 
  \begin{itemize}
   \item Narrower (add to the top and bottom)
   \item Wider (cut top and bottom)
   \item Shorter (add to the sides)
   \item Taller (cut sides)
  \end{itemize}
  \item Mouse zoom 
  \begin{itemize}
   \item Same ratio(show exactly what is marked)
   \item High rectangle(add extra to fit ratio)
   \item Wide rectangle(add extra to fit ratio)
  \end{itemize}
\end{itemize}
\subsection{System test coverage table}
\begin{centering}
\begin{longtable}{|p{0.20\textwidth}|p{0.30\textwidth}|p{0.30\textwidth}|p{0.20\textwidth}|}
\hline
Test & Instruction & Expected result & Actual result\\
\hline
Zoom in & Press the zoom in button on the navigation panel & The map should zoom
in on the center of the map & As expected\\
\hline
Zoom out & Press the zoom in button on the navigation panel twice. Then press
the zoom out button & The map should out but have the same spot centered & As
expected\\
\hline
\hline
Pan:north & Press the up-button on the navigation panel & The map should pan a
bit to the north & As expected\\
\hline
Pan:south & Press the down-button on the navigation panel & The map should pan a
bit to the south & As expected\\
\hline
Pan:east & Press the right-button on the navigation panel & The map should pan a
bit to the east & As expected\\
\hline
Pan:west & Press the left-button on the navigation panel & The map should pan a
bit to the west & As expected\\
\hline
\hline
Minimum zoom & Press the zoom in button until it doesn't zoom in any further &
The view should still be far enough out to see a couple of roads (if there are
roads in that area) & As expected\\
\hline
Maximum zoom & Zoom in \textbf{five} times and then zoom out until it doesn't
zoom out any further & The map should show the original view (max view) & As expected\\
\hline
\hline
Pan out of map: north & Zoom in \textbf{two} times and press the up-button on
the navigation panel \textbf{seven} times & The map shouldn't change on the last
press, thus still showing some roads & As expected\\
\hline
Pan out of map: south & Zoom in \textbf{two} times and press the down-button on
the navigation panel \textbf{seven} times & The map shouldn't change on the last
press, thus still showing some roads & As expected\\
\hline
Pan out of map: east & Zoom in \textbf{two} times and press the right-button on
the navigation panel \textbf{six} times & The map shouldn't change on the last
press, thus still showing some roads & As expected\\
\hline
Pan out of map: west & Zoom in \textbf{two} times and press the left-button on
the navigation panel \textbf{six} times & The map shouldn't change on the last
press, thus still showing some roads & As expected\\
\hline
\hline
Hotkey:ESCAPE & Press the ESCAPE key on the keyboard & The view should reset to
the original view (max view) & As expected\\
\hline
Hotkey:C & Place a marker on the map by pressing the left mouse-button somewhere
on the map. Press the C key on the keyboard & The marker should disappear & As
expected\\
\hline
Hotkey:I & Press the I key on the keyboard & The map should zoom in on the
center of the map & As expected\\
\hline
Hotkey:O & Press the I key on the keyboard, then press the O key on the keyboard
& The map should zoom out to the original view (max view) & As expected\\
\hline
Hotkey:ARROW UP & Press the I key on the keyboard, then press ARROW UP & With
the last keypress, the map should a bit to the north & As expected\\
\hline
Hotkey:ARROW DOWN & Press the I key on the keyboard, then press ARROW DOWN &
With the last keypress, the map should a bit to the south & As expected\\
\hline
Hotkey:ARROW LEFT & Press the I key on the keyboard, then press ARROW LEFT &
With the last keypress, the map should a bit to the west & As expected\\
\hline
Hotkey:ARROW RIGHT & Press the I key on the keyboard, then press ARROW RIGHT &
With the last keypress, the map should a bit to the east & As expected\\
\hline
\hline
One Marker & Place a marker on the map by pressing the left mouse-button
somewhere on the map & You should see a marker where you clicked, but no routes
& As expected\\
\hline
Two markers & Place a marker on the map by pressing the left mouse-button
somewhere on the map, then another somewhere else. & You should see two markers
where you clicked and a route between them & As expected\\
\hline
Two markers (same Node) & Zoom in on a road. Place a marker on the map and
another right next to it. & You should not see any route. & As expected\\
\hline
Multiple Markers & Place a marker on the map by pressing the left mouse-button
somewhere on the map, then place two more at other spots. & You should see three
markers where you clicked, and the routes:  first-\textgreater second and
second-\textgreater third & As expected\\
\hline
\hline
Clear markers & Place a marker on the map by pressing the left mouse-button
somewhere on the map. Press the Clear Markers button on the Route Options panel
& The marker should disappear & As expected\\
\hline
\hline
Change mode & Place a marker on the map by pressing the left mouse-button
somewhere on the map, then another somewhere else. Then select Bike mode on the
Route Options panel & The new mode should be shown as selected, and the route
should be recalculated with the new mode and  probably change & As expected\\
\hline
\hline
Closest node & Place a marker far away from any roads, then another one near
roads & It should find a path from the closest node to where you clicked first,
even though it is far away. & As expected\\
\hline
Closest node: relative to mode & Place a marker close to a path and another some
distance away. & When in Car mode it should find the closest regular road to
start from, when in Bike mode it should start at the path. & As expected\\
\hline
\hline
Right direction on one-way road & Place a marker near the beginning of a one-way
road, and then place another near the end. & The route should travel directly
across the one-way road. & As expected\\
\hline
Wrong direction on one-way road & Place a marker near the end of a one-way road,
and then place another near the start. & The route should not travel directly
across the one-way road, but somewhere around it. & As expected\\
\hline
\hline
Resize:Narrower & Select the right border of the window and the window
\textbf{narrower} & It should show more at the top and bottom to adjust for the
changed ratio. & As expected\\
\hline
Resize:Wider & Select the right border of the window and the window
\textbf{wider} & It should show more at the top and bottom to adjust for the
changed ratio. & As expected\\
\hline
Resize:Shorter & Select the bottom border of the window and the window
\textbf{shorter} & It should show more at the top and bottom to adjust for the
changed ratio. & As expected\\
\hline
Resize:Narrower & Select the bottom border of the window and the window
\textbf{taller} & It should show more at the top and bottom to adjust for the
changed ratio. & As expected\\
\hline
\hline
Mouse zoom: Correct zoom & Drag a rectangle on the map with about the same ratio
as the window, by pressing the left mouse-button somewhere and drag until having
the right size. & The map should now show approximately the marked spot. & As
expected\\
\hline
Mouse zoom: Tall rectangle & Drag a tall rectangle on the map & The map should
show what marked but show more at the sides to adjust for the difference in
ratio. & As expected\\
\hline
Mouse zoom: Tall rectangle & Drag a tall rectangle on the map & The map should
show what marked but show more at the top and bottom to adjust for the
difference in ratio. & As expected\\
\hline
\end{longtable}
\end{centering}