\documentclass{report}

\usepackage[latin1]{inputenc}
\usepackage[english]{babel}
%\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{mathtools}
\usepackage{appendix}
\usepackage{nameref}
\usepackage{fancyhdr}
\usepackage{mathtools}
\usepackage[final]{pdfpages}
\usepackage[font=sl]{caption}

\pagestyle{fancy}
\cfoot{\thepage\ of ??}

\setlength{\parindent}{0pt}
\setlength{\parskip}{1.8ex plus 0.5ex minus 0.2ex}
\newcommand{\class}[1]{\textsf{#1}}
\renewcommand{\chaptermark}[1]{\markboth{\MakeUppercase{\thechapter.\ #1}}{}}

\title{Map of Denmark\\
\normalsize{\textit{First-Year Project, Bachelor in Software Development, \\IT
Univ. of Copenhagen}}}
\author{
Group 12\\
Jakob Melnyk jmel@itu.dk\\
Niklas Hansen nikl@itu.dk\\
Emil Juul Jacobsen ejuu@itu.dk\\
Jens Dahl Møllerhøj jdmo@itu.dk\\
\\
Supervisor: Lars Birkedal\\
Advisors: Jonas Brabrand
Jensen and Filip Sieczkowski
}
\date{May 25th, 2011}

\begin{document}
\maketitle
\tableofcontents
\pagebreak
\chapter{Preface}
\label{PRE}
This report is the result of a project at the bachelor in Software Development 
on the IT University of Copenhagen spanning from early March 2011 to late May
2011. The project was given as a first semester project in groups of 4 to 5
randomly picked students. 2.5 months of the semester was set aside for this
project. The time not spent on the report was spent on planning, coding, 
thorough testing and bugfixing of the actual program.

\include{chapters/product/Background}
\include{chapters/product/UI-Analysis}
\include{chapters/product/Implementation}
\include{chapters/product/TechnicalUML}
\include{chapters/product/Tests}
\include{chapters/product/Manual}
\chapter{Product conclusion}
\label{PRC}
We believe our product live up to the project requirements described in chapter
\ref{BG} \class{\nameref{BG}}. Our program also runs fast enough when using the
interface. We tested this on both a fast computer and an older, slower computer
and we did not feel it was cumbersome to use the program, even on the slower
computer. We did not thoroughly test this however, and we cannot guarantee that
there will not be circumstances where our program will run slowly.
 
The system tests were done on a Windows 7 computer and because of this, we
cannot be certain that all features work on other operating systems. However, 
two of our group members use Mac OS X and they have experienced no problems 
with our program.

We did all of our testing internally. For a even more thorough testing of our
software, we could have asked other groups to test the software for us, so that
we could get a different look on the tests. We did no usability testing
throughout the project, and while our user interface is simple, we should have
tested to make sure we designed our interface in the best way possible.

\section{Issues in the software}
\label{PRC-BUGS}
We have discovered a few bugs our software that did not show itself through our
testing, but instead manifested with regular use of the software.

We have a bug in our zoom-function, which enables the user to zoom very far in
by zooming in, then resizing the window. This caused the program to be locked at
a very far zoomed in view, but we chose to let the user zoom out when they are
zoomed far in. The problem with zooming too far in can still happen, but the
view is not locked when it happens.

\section{Future features}
\label{PRC-FF}
If we had had time, we would have included more features in our program. We feel
our program could still do with some fine tuning for it to be of real use
outside of living up to the requirements. During development, we have focused on
getting the basic requirements to work proberly, before working at more advanced
feautures. This have made our process more secure, because we were sure not to
forget the important things. The advanced features that we would have like to
implement is described here:

We would have liked to have implemented a ``road search'' function, enabling the
user to search for the name of a road and place a marker there. In addition, we
would have like to implement the option for the user to view a route description
with turns. We were actually working on making route description, but we couldn't 
get it nice and pretty enough in time, so we felt we would be better off without it.

To make the map look nicer, we attempted to implement a function for the map to
create an outline of Denmark, separating the land from the sea, so that it was more 
obvious what is land and what is water. It would first of all make our program prettier, 
but with it we would be able to draw fewer roads when zoomed out, resulting in better 
performance. We would also have liked to make a logo for our program, but we did not 
get around to implementing it.

\include{chapters/process/Constitution}
\include{chapters/process/Diary}
\include{chapters/process/Worksheets}
\chapter{Process description and reflection}
\label{PDF}
As a group we have had some ups and downs during the last two and a half months
we have been on this project. Filip from our group dropped out early May, so
when we were about to start working on this report, we were down to four group
members.

We kept a pretty tight structure as far as having meetings pretty often, but
sometimes we got a bit unfocused during the meetings. We changed from meeting
two days of six hours to three days of four hours once lectures stopped in
early May, and this helped a lot. While our diary was not kept up-to-date
properply, our meeting documents helped us have a good idea of what was going with everyone in
terms of what they were doing on the project. The meeting documents can be found
in appendix \ref{APP-WS-MD} on page \pageref{APP-WS-MD}.

A lot of the work on the project - especailly writing this report and coding the
program - was done at home. At meetings we discussed different solutions etc.
and then we gave eachother homework until the next meeting. We were a bit sloppy
getting things done on time, as there was rarely a day where everyone had done
all of their ``homework''.

We had an internal evaluation where everyone got a chance to vent about how we
were doing on the project, how we were working together as a group and if anyone
had any problems with how the other members in the group worked, this was the
time to say it. Doing this internal evaluation really gave everyone a chance to
vent and it was also during this evaluation - where Filip was not present - that
we decided that he really could not be part of the group if he did not show for
meetings. It was good for us to get these problems addressed before they got any
worse and started affecting our work.

When we first sat down and created our ``Group norms'' (see \ref{GN} on page
\pageref{GN}), we decided that we just wanted everyone to do their best. Even
though we have members who are more dedicated and ambitious when it comes to
this project, they respected that everyone had to work at their own pace and
that working together on a bigger project like this was not something all
members of the group were used to.

As previously mentioned we wanted to use the meeting documents to keep track of
time and when we needed to be done with the different parts of the project. A
bigger plan could have been a good thing to have had, so we did not suddenly get
surprised by needing to have working code to hand in for the different parts of
the project. 

Not only did the meeting documents work as our diary, they helped us remember
what we was currently working on. If a one of the groupmembers was not present
at a meeting, he got updates about our work by looking at the document.
Since we had described the homework each member had to do, there was no doubt
about what you had to work on.

In the final part of the project, we decided that we wanted an, at least for us,
early feature and code freeze, so that we could focus on getting the report done
early. The schedule for the last week of the project can be found in appendix
\ref{APP-LW} on page \pageref{APP-LW}. The advantage of having an early code
freeze was that we had a reasonable amount of time to polish the report. The disadvange was that we did not manage to
implement all the features we wanted to.

We are satisfied with how our project turned out. While we could have worked a
bit more efficiently at times, the product turned to be want we wanted.

As mentioned in the product conclusion, there were several parts we could
improve in terms of the product itself, but that is often the case with projects
like this.

\begin{thebibliography}{99}
\bibitem{algs4}
Robert Sedgewick and Kevin Wayne. \emph {Algorithms, Fourth Edition}. Preliminary Edition Fall 2010. Addision-Wesley 2010.
\bibitem{httpalgs4}
Algorithms, Fourth Edition homepage: http://algs4.cs.princeton.edu/24pq/IndexMinPQ.java ; Date:
May 23rd, 2011.
\bibitem{MD5}
\emph{MD5Checksum homepage}: http://www.rgagnon.com/javadetails/java-0416.html ;
Date: May 23, 2011.
\end{thebibliography}
\pagestyle{plain}
\include{chapters/appendix/Appendix}
\end{document}