\appendix
\addappheadtotoc
\chapter{Tests}
This section covers tables and other appendices for our \class{Tests} chapter in
the report.
\section{JUnit tests}
\label{APP-TE-JU}
\subsection{PointMethods test table}
\label{APP-TE-JU-PM}
The table in this section shows the full extent of our JUnit test coverage of
the \class{PointMethods} class. Any variable that is described in the
example column in the row of the method name is used in all the tests for that
method.

\input{chapters/appendix/tables/PointMethods}
\pagebreak
\subsection{RectangleMethods test table}
\label{APP-TE-JU-RM}
The table in this section shows the full extent of our JUnit test coverage of
the \class{RectangleMethods} class. Any variable that is described in the
example column in the row of the method name is used in all the tests for that
method.

\input{chapters/appendix/tables/RectangleMethods}
\pagebreak
\subsection{Model test table}
\label{APP-TE-JU-MO}
The table in this section shows the tests we have made as JUnit tests to cover
the different methods in the \class{Model} class. Input for methods that take
\class{Node}s as input are given as their index in this coverage table.

\input{chapters/appendix/tables/Model}

\pagebreak
\section{System tests}
\label{APP-TE-ST}

\input{chapters/appendix/tables/System_tests}

\chapter{Worksheets}
\label{APP-WS}
This appendix covers our meeting documents and our spreadsheet diary. We
included these because they describe most of the work that we have done and when
we did it.

\section{Meeting documents}
\label{APP-WS-MD}
\input{chapters/appendix/other/meetingdocuments}

\section{Spreadsheet diary}
\label{APP-SS}
This appendix covers the diary we made in spreadsheet format in the time working
on this project. It is not a complete diary, as we did not always keep it up to
date. 

\input{chapters/appendix/tables/SpreadsheetDiary}