\chapter{Manual}
\label{MAN}

\section{Navigation}
\label{MAN-N}
The navigation of the map works pretty straight forward. At startup, the entire
country of Denmark is shown. Now, we can move around the map with both the
direction buttons in the top left corner, and the arrow keys. To move west,
click the button Ò<Ó or press the left arrow key. This goes for all 4
directions.

\section{Zoom}
\label{MAN-Z}
To zoom-in on the map, click the Ò+Ó button in the navigation
panel. To zoom-in on a specific area, click and drag a rectangle around that
area on the map. A blue transparent rectangle will show you the selected area.
To zoom-in, release the mousebutton. If you want to zoom-in on Copenhagen,
click the upper left corner of the city, and drag the cursor to the lower right
corner.

\section{Route find}
\label{MAN-RF}
To find a route from one point to another, you must specify a start and an end
location. Click anywhere on the map to choose your start location. A light blue
marker will appear, containing the number Ò1Ó. To choose your end location,
click at another location. A marker containing the number Ò2Ó will appear. The
best route from 1 to 2 will be calculated, and shown on the map as a blue path.
To extend your route with more markers, you can click at a new location on the
map. You can repeat this an unlimited amount of times. You can delete one of
your markers by clicking at its root.

\section{Bike/car}
\label{MAN-BC}
When calculating routes, it is important to specific which form of
transportation you wish to use. Choose your preferred style of transportation by
selecting the corresponding radio button.

\section{Resize}
\label{MAN-RS}
To resize the map, drag the window as you would with any other application. The
map will automatic adjust to the new size of the window.