\chapter{User Interface analysis}
\label{UIA}
In this chapter we describe our decisions and present our analysis and
arguments regarding some of the features that we find interesting.

\section{User interface as a whole}
\label{UIA-UIW}


\section{Interesting implemented features}
\label{UIA-IF}
This section presents some of the interesting features we have implemented.
\subsection{Zoom}
\label{UIA-IF-Z}
We have several options for zooming in and out on the map. As described in
section \ref{BG-R-PR} on page \pageref{BG-R-PR}, it was required that we made it
possible to zoom by dragging a box around the part of the map the user wants to
view.

In addition to the option of using the mouse to zoom, we have implemented a
zoom-in and out function on the GUI and a hotkey for zooming out to the original
view. 

We felt that we really needed a zoom out function, so that a user did not
need to close the program and start it again, when the user wants to view the
map further zoomed out. A combination of the zoom in and out functions helps the
user a lot when navigating the map.

\subsection{Navigation}
\label{UIA-IF-N}
We have made it possible for the user to navigate the map by scrolling 

\subsection{Hotkeys}
\label{UIA-IF-H}
\subsection{Markers}
\label{UIA-IF-M}
\subsection{Bike/car}
\label{UIA-IF-BC}

\section{Not implemented}
\label{UIA-NF}
This section presents some of the features we have chosen not to implement.
These features are not in the final program, because we did not feel there were
compelling arguments for implementing them.
\subsection{Choice of roads to be displayed}
\label{UIA-NF-CRD}
\subsection{Smooth scrolling}
\label{UIA-NF-SS}
\subsection{Dynamic route finding}
\label{UIA-NF-DRF}